Ceph Parallel File System Evaluation Report

### 2013-08-20 ceph-eval.tex
add parameter notes for sweeping test

We ran a script written by Inktank for internal Ceph testing to perform
sweeps over Ceph configuration parameters to examine how different
tuning options affect performance on the DDN platform. The result of this
parameter probing is illustrated in Figure~\ref{fig:parametric}.

@@

>>>>

We ran a script written by Inktank for internal Ceph testing to perform
sweeps over Ceph configuration parameters to examine how different
tuning options affect performance on the DDN platform. The result of this
parameter probing is illustrated in Figure~\ref{fig:parametric}. Please refer
to Appendix E for explanations of these probed parameters.

@@

\section*{Appendix E - Tuning Parameters}
\addcontentsline{toc}{section}{Appendix E - Tuning Parameters}

For parameter sweep, here are the settings we iterated through.  Some of these
are "compound" settings where we increased or decreased multiple things in the
ceph.conf file at the same time to reduce the number of permutations that would
need to be tested.

\input{tuning.txt}
